### 2011-09-19 doc/theses/vitasek/chapter-4-2-experiments-results.tex
Thesis: in progress.

We should note that the combination best CH - best IH found this way does not necessarily need to be the best one, because we find it using a hungry approach.

>>>>

We should note that the combination \textit{best CH - best IH} found this way does not necessarily need to be the best one overall, because we find it using a hungry approach.
